### 2018-02-07 highlighted.tex

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University, Montreal, Quebec, Canada \\
\textbf{2} Univ Lyon, UJM-Saint-Etienne, Saint-\'{E}tienne, France \\
\textbf{3} The University of Texas at Austin, Austin, Texas, USA \\
\textbf{4} The University of Texas at Tyler, Tyler, Texas, USA \\
\textbf{5} CSIRO Oceans and Atmosphere, Hobart, Tasmania, Australia \\
\textbf{6} University of Waterloo, Waterloo, Ontario Canada \\
\textbf{7} DataCamp, Toronto, Ontario, Canada, gvwilson@third-bit.com \\

@@

\noindent
Box 1: Learner Profile

Jorge has just moved from Costa Rica to Canada to study agricultural engineering.
While fluent in both Spanish and English,
he has a hearing disability that sometimes makes it hard for him to understand lectures,
particularly in noisy environments.
Other than using Excel, Word, and the Internet,
Jorge's most significant previous experience with computers is
helping his sister build a WordPress site for the family business.

Jorge needs to measure properties of soil from nearby farms
using a handheld device that sends text files to his computer.
Right now, Jorge has to open each file in Excel,
crop the first and last points,
and calculate an average.
This workshop will show Jorge how to write a little Python program
to read the data,
select the right values from each file,
and calculate the required statistics.

@@

\bibitem{proghist}
Afanador-Llach MJ, Baker J, Crymble A, Gayol V, Gibbs F, Lincoln M, McDaniel C, Milligan I, Parr J, Castro AR, Knuppel AS, Visconti A, Walsh B, Wieringa J.
\newblock Programming Historian,
\newblock \url{https://programminghistorian.org/}.

>>>>

% Highlight changes.
\usepackage{soul}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} \hl{Douglas Mental Health University Institute, McGill University, Montreal, Quebec, Canada} \\
\textbf{2} \hl{Univ Lyon, UJM-Saint-Etienne, Saint-\'{E}tienne, France} \\
\textbf{3} \hl{The University of Texas at Austin, Austin, Texas, USA} \\
\textbf{4} \hl{The University of Texas at Tyler, Tyler, Texas, USA} \\
\textbf{5} \hl{CSIRO Oceans and Atmosphere, Hobart, Tasmania, Australia} \\
\textbf{6} \hl{University of Waterloo, Waterloo, Ontario Canada} \\
\textbf{7} \hl{DataCamp, Toronto, Ontario, Canada, gvwilson@third-bit.com} \\

@@

\noindent
\hl{Box 1: Learner Profile}

\hl{Jorge has just moved from Costa Rica to Canada to study agricultural engineering.
While fluent in both Spanish and English,
he has a hearing disability that sometimes makes it hard for him to understand lectures,
particularly in noisy environments.
Other than using Excel, Word, and the Internet,
Jorge's most significant previous experience with computers is
helping his sister build a WordPress site for the family business.}

\hl{Jorge needs to measure properties of soil from nearby farms
using a handheld device that sends text files to his computer.
Right now, Jorge has to open each file in Excel,
crop the first and last points,
and calculate an average.
This workshop will show Jorge how to write a little Python program
to read the data,
select the right values from each file,
and calculate the required statistics.}

@@

\bibitem{proghist}
\hl{Afanador-Llach MJ, Baker J, Crymble A, Gayol V, Gibbs F, Lincoln M, McDaniel C, Milligan I, Parr J, Castro AR, Knuppel AS, Visconti A, Walsh B, Wieringa J.}
\newblock \hl{Programming Historian,}
\newblock \url{https://programminghistorian.org/}.
